
\documentclass{article} % For LaTeX2e
\usepackage{iclr2025_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}

% \usepackage{booktabs} 
% \usepackage{graphicx}
% \usepackage{xcolor}
% \usepackage{colortbl}
% \usepackage{amsmath}
% \usepackage{floatrow}
% \floatsetup[table]{capposition=top}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[utf8]{inputenc}
% \usepackage{geometry}
% \usepackage{graphics}
\usepackage{multirow}
\usepackage{rotating}
% \usepackage[caption=false]{subfig}
\usepackage{verbatim}
\usepackage{booktabs}
\usepackage{array}
\usepackage{textcomp, gensymb}
\usepackage{diagbox}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{setspace}
% \usepackage{geometry}
% \usepackage{graphics}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{diagbox}
\usepackage{mathtools}
\usepackage{wrapfig}
\usepackage{diagbox} 
\usepackage{wrapfig,lipsum,booktabs}
\usepackage{caption}
\usepackage{appendix}
\usepackage{enumitem}
% \hypersetup{ 
%     colorlinks=true, 
% } 
% \usepackage{subcaption}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
% \usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\usepackage{color}
%\definecolor{citecolor}{HTML}{0071bc}
\usepackage{colortbl}
\usepackage{array}
\usepackage{booktabs} % For \hline and \shline (if defined)
\usepackage{graphicx} % For figures
\usepackage{amsmath} % For math and text formatting
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{subcaption}
\usepackage{xspace}
% \newcommand{\paperName}{Light Field Transformer}

% \title{{\paperName}: Scalable and Generalizable Novel View Synthesis without 3D Representation}

% \newcommand{\hanwen}[1]{{\color{magenta}[hanwen: #1]}}
% \newcommand{\zexiang}[1]{{\color{red}[ZX: #1]}}
% \newcommand{\kai}[1]{\noindent {\color{red} {\bf Kai:}     {#1}}}
% \newcommand{\hao}[1]{{\color{brown}[Hao: #1]}}
% \newcommand{\haian}[1]{\noindent {\color{green} {\bf Haian:}     {#1}}}
% \newcommand{\sai}[1]{\noindent {\color{cyan} {\bf Sai:}     {#1}}}


\newcommand{\paperName}{LVSM\xspace}

\title{{\paperName}: A Large View Synthesis Model with \\ Minimal 3D Inductive Bias}


\author{%
\textbf{Haian Jin$^{1}$}~~~
\textbf{Hanwen Jiang$^{2}$}~~~
\textbf{Hao Tan$^{3}$}~~~
\textbf{Kai Zhang$^{3}$}~~~
\textbf{Sai Bi$^{3}$}~~~
\textbf{Tianyuan Zhang$^{4}$}\\
\textbf{Fujun Luan$^{3}$}~~~
\textbf{Noah Snavely$^{1}$}~~~
\textbf{Zexiang Xu$^{3}$} 
\\
$^{1}$Cornell University \ 
$^{2}$The University of Texas at Austin \
\\
$^{3}$Adobe Research \ 
$^{4}$Massachusetts Institute of Technology
}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}


\newcommand{\tabref}[1]{\noindent Tab. \ref{#1}}
\newcommand{\img}{\mathbf{I}}
\newcommand{\tok}{\mathbf{T}}
\newcommand{\boldstart}[1]{\noindent\textbf{#1}}
\newcommand{\boldstartspace}[1]{\medskip\noindent\textbf{#1}}

\iclrfinalcopy % Uncomment for camera-ready version

\begin{document}
% \vspace{-10mm}
\maketitle
\vspace{-5mm}
\begin{abstract}
\vspace{-3mm}
We propose the Large View Synthesis Model (LVSM), a novel transformer-based approach for scalable and generalizable novel view synthesis from sparse-view inputs. We introduce two architectures: (1) an encoder-decoder LVSM, which encodes input image tokens into a fixed number of 1D latent tokens, functioning as a fully learned scene representation, and decodes novel-view images from them; and (2) a decoder-only LVSM, which directly maps input images to novel-view outputs, completely eliminating intermediate scene representations. Both models bypass the 3D inductive biases used in previous methods---from 3D representations (e.g., NeRF, 3DGS) to network designs (e.g., epipolar projections, plane sweeps)---addressing novel view synthesis with a fully data-driven approach. 
While the encoder-decoder model offers faster inference due to its independent latent representation, the decoder-only LVSM achieves superior quality, scalability, and zero-shot generalization, outperforming previous state-of-the-art methods by 1.5 to 3.5 dB PSNR. Comprehensive evaluations across multiple datasets demonstrate that both LVSM variants achieve state-of-the-art novel view synthesis quality. Notably, our models surpass all previous methods even with reduced computational resources (1-2 GPUs). Please see our website for more results: \textcolor{red}{\tt\small\url{https://haian-jin.github.io/projects/LVSM/}}.
\end{abstract}
\vspace{-3mm}
\input{sections/1_intro}
\input{sections/2_related}
\input{sections/3_method}
\input{sections/4_exp}

\vspace{-4mm}
\section{Conclusion}
\vspace{-4mm}
In this work, we presented the Large View Synthesis Model (LVSM), a transformer-based approach designed to minimize 3D inductive biases for scalable and generalizable novel view synthesis. Our two architectures—encoder-decoder and decoder-only—bypass physical-rendering-based 3D representations like NeRF and 3D Gaussian Splatting, allowing the model to learn priors directly from data, leading to more flexible and scalable novel view synthesis. The decoder-only LVSM, with its minimal inductive biases, excels in scalability, zero-shot generalization, and rendering quality, while the encoder-decoder LVSM achieves faster inference due to its fully learned latent scene representation. Both models demonstrate superior performance across diverse benchmarks and mark an important step towards general and scalable novel view synthesis in complex, real-world scenarios.

\paragraph{Acknowledgements.} We thank Kalyan Sunkavalli for helpful discussions and support. This work was done when Haian Jin, Hanwen Jiang, and Tianyuan Zhang were research interns at Adobe Research.  This work was also partly funded by the National Science Foundation (IIS-2211259, IIS-2212084).
\bibliography{iclr2025_conference}
\bibliographystyle{iclr2025_conference}

\clearpage
\appendix

\input{sections/5_appendix}


\end{document}
